### 2023-03-07 main.tex

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%\usepackage{microtype}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix} 
\usepackage{comment}
\numberwithin{equation}{section}

@@

We consider a connecAt each site $x\in V$, we describe the occupation with an $N-$dimensional vector in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$. On each vertex we allow maximal occupancy $\nu\in \mathbb{N}$. Then, the configuration space is

@@

Consider the $gl(N)$ Lie algebra with with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{bc}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ with $\lambda_i\in \mathbb{N}$ and  $\lambda_i\geq \lambda_{i+1}$.
We are interested in the symmetric finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}
\end{equation} 
The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition:
\begin{equation}
	M= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space of the representation $\mathbb{C}^{M}$ are the column vectors 
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle
\end{equation}
%where $\sum_{k=1}^{N}n_{i}=\nu$. 
This basis vector satisfy the orthogonality relation
\begin{equation}\label{ortho}
    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{k=1}^{N}\delta_{m_{k},n_{k}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m\rangle$ and $\delta_{m_{k},n{k}}$ is the Kronhecker delta. 
The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle\quad a=b
	\end{cases}
\end{equation}  
One can check that the generators defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. The Cartan element $E_{aa}$ conserves the number of particles of type $a$. 
\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\mu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process characterized by the generator \eqref{Generator}. We consider the state space \eqref{stateSpace} composed by

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%\usepackage{microtype}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix}
\usepackage{comment}
\numberwithin{equation}{section}
\numberwithin{equation}{subsection}

@@

We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
At each site $x\in V$, we describe the occupation with an $N-$dimensional vector in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$. On each vertex we allow maximal occupancy $\nu\in \mathbb{N}$. Then, the configuration space is

@@

Consider the $gl(N)$ Lie algebra with with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{bc}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
{\color{red}The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$. We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.}
We are interested in the {\em symmetric} finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}
\end{equation} 
The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition:
\begin{equation}
	M= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space of the representation $\mathbb{C}^{M}$ are the column vectors 
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle
\end{equation}
%where $\sum_{k=1}^{N}n_{i}=\nu$. 
This basis vector satisfy the orthogonality relation
\begin{equation}\label{ortho}
    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{k=1}^{N}\delta_{m_{k},n_{k}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m\rangle$ and $\delta_{m_{k},n_{k}}$ is the Kronhecker delta. 
The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle\quad a=b
	\end{cases}
\end{equation}  
One can check that the generators defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. The Cartan element $E_{aa}$ conserves the number of particles of type $a$.

\noindent
\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\mu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process characterized by the generator \eqref{Generator}. We consider the state space \eqref{stateSpace} composed by
